\bf Calibration of P-values for calibration and for deviation of a subpopulation from the full population

### 2022-08-19 tex/paper.tex
formatting

\begin{theorem}
\label{kucal}
Assume the null hypothesis that the subpopulation has no expected deviation
from the full population (that is, $\E[R_k] = r(S_k)$
for $k = 1$,~$2$, \dots, $n$) and that the third moment obeys
$\E[|R_k - r(S_k)|^3] \le C (v(S_k))^{3/2}$ for $k = 1$,~$2$, \dots, $n$,
where $C$ is a finite positive real number that does not depend on $n$.
Suppose also that the scores $S_1$, $S_2$, \dots, $S_n$ are all distinct
for each $n$ and
$\max_{1 \le k \le n} v(S_k) \cdot (W_k)^2 / \sum_{j=1}^n v(S_j) \cdot (W_j)^2$
converges to 0 in the limit as $n$ becomes large.
Then, with $H$ defined in~(\ref{kuiper})
and $\sigma$ defined in~(\ref{general}),
the normalized Kuiper statistic $H/\sigma$
for measuring deviation of a subpopulation from the full population
converges in distribution to the range of the standard Brownian motion
over the unit interval $[0, 1]$.
(The range is the maximum minus the minimum.)
The normalized Kuiper statistic $H/\sigma$ for measuring calibration
converges in distribution to the range of the standard Brownian motion
over the unit interval $[0, 1]$, too, when taking the expected response
at each score to be equal to the score, that is, $r(s) = s$
for every score $s$.
\end{theorem}

>>>>

\begin{theorem}
\label{kucal}
Assume the null hypothesis that the subpopulation has no expected deviation
from the full population (that is, $\E[R_k] = r(S_k)$
for $k = 1$,~$2$, \dots, $n$) and that the third moment obeys
$\E[|R_k - r(S_k)|^3] \le C (v(S_k))^{3/2}$ for $k = 1$,~$2$, \dots, $n$,
where $C$ is a finite positive real number that does not depend on $n$.
Suppose also that the scores $S_1$, $S_2$, \dots, $S_n$ are distinct
for each $n$ and
$\max_{1 \le k \le n} v(S_k) \cdot (W_k)^2 / \sum_{j=1}^n v(S_j) \cdot (W_j)^2$
converges to 0 in the limit as $n$ becomes large.
Then, with $H$ defined in~(\ref{kuiper})
and $\sigma$ defined in~(\ref{general}),
the normalized Kuiper statistic $H/\sigma$
for measuring deviation of a subpopulation from the full population
converges in distribution to the range of the standard Brownian motion
over the unit interval $[0, 1]$.
(The range is the maximum minus the minimum.)
The normalized Kuiper statistic $H/\sigma$ for measuring calibration
converges in distribution to the range of the standard Brownian motion
over the unit interval $[0, 1]$, too, when taking the expected response
at each score to be equal to the score, that is, $r(s) = s$
for every score $s$.
\end{theorem}
